Contextual Combinatorial Cascading Bandits

### 2015-11-19 contextual combinatorial cascading bandits.tex
update main theorem and several useful lemmas

Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all items in $E$. The UCB of item $a$ at time $t$ is defined as:
\begin{equation}
	\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}X_{t,a} + \beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
\end{equation}
By theorem \ref{thm:theta_estimate}, it holds that
\begin{lemma}
	For any $\delta > 0$, with high probability at least $1 - \delta$, for any $t>0$,
	$$
		0 \leq \bU_t(a) - \theta_*^{\top}X_{t,a} \leq 2\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
	$$
\end{lemma}
\begin{proof}
	\begin{align*}
	\abs{\hat{\theta}_{t-1}^{\top}X_{t,a} - \theta_*^{\top}X_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_*}_{\bV_{t-1}} \norm{X_{t,a}}_{\bV_{t-1}^{-1}} \\
	&\leq \beta_{t}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
	\end{align*}
\end{proof}

@@

Let
\begin{equation}
	C_\gamma = \sum_{k=1}^{K} \gamma_k^2.
\end{equation}

@@

\begin{lemma}
	$1\geq \gamma_1\geq \cdots \geq \gamma_K > 0$. If we have $w \leq w'$, then for any $A$,
	$$
		f(A, w) \leq f(A, w').
	$$
\end{lemma}
\begin{proof}
	It suffices to prove when $A = \{1,...,m\}, m\leq K$. First, 
	\begin{align*}
		& f(A, w)=\sum_{k=1}^m \gamma_k\prod_{i=1}^{k-1}(1-w_i)w_k\\
		&\geq f(K,w_1,...,w_{K-1},w_K'). 
	\end{align*}
	For $f(K, w_1,...,w_k,w_{k+1}',...,w_K')\geq f(K;w_1,...,w_k',...,w_K')$, it is equivalent to prove that $(w_k-w_k')(1-\gamma(w_{k+1}'+(1-w_{k+1}')w_{k+2}'+...))>0$.
\end{proof}

\begin{lemma}
	$\sum_{k=1}^K \gamma^{k-1}\prod_{i=1}^{k-1}(1-(a_i+c_i))(a_k + c_k) \leq \sum_{k=1}^K \gamma^{k-1}\prod_{i=1}^{k-1}(1-a_i)a_k + \sum_{k=1}^K \gamma^{k-1}c_k$.
\end{lemma}
This lemma can be proved by induction. Need to change definition of Ut to min(Ut,1). So similarly, we can have

\begin{lemma}
	$E[\Delta_{\bA_t}|\cH_t] \leq \frac{2}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$
\end{lemma}

>>>>

	Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all items in $E$. The UCB of item $a$ at time $t$ is defined as:
	\begin{equation}
	\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}X_{t,a} + \beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
	\end{equation}
	By theorem \ref{thm:theta_estimate}, it holds that
	\begin{lemma}
		\label{lem:estimateU}
		For any $\delta > 0$, with high probability at least $1 - \delta$, for any $t>0$,
		$$
		0 \leq \bU_t(a) - \theta_*^{\top}X_{t,a} \leq 2\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
		$$
	\end{lemma}
	\begin{proof}
		\begin{align*}
		\abs{\hat{\theta}_{t-1}^{\top}X_{t,a} - \theta_*^{\top}X_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_*}_{\bV_{t-1}} \norm{X_{t,a}}_{\bV_{t-1}^{-1}} \\
		&\leq \beta_{t}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
		\end{align*}
	\end{proof}

@@

	\section{Analysis}
	Let
	\begin{equation}
	C_\gamma = \sum_{k=1}^{K} \gamma_k^2.
	\end{equation}

	\begin{lemma}
		\label{lem:increasing} 
		$1\geq \gamma_1\geq \cdots \geq \gamma_K > 0$. If we have $w \leq w'$ as column vectors in $\RR^L$, then for any $A\in\cS$,
		$$
		f(A, w) \leq f(A, w').
		$$
	\end{lemma}
	\begin{proof}
		Because for $1 \leq k \leq m$,
		\begin{align*}
		&~~\gamma_k - \sum_{i=k+1}^m \gamma_i\prod_{j=k+1}^{i-1}(1-w_j)w_i\\
		&\geq \gamma_k (1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1-w_j)w_i) \\
		&=\gamma_k \prod_{i=k+1}^{m}(1-w_i)\geq 0,
		\end{align*}
		then
		\begin{align*}
		&~~\gamma_k w_k + (1-w_k)\sum_{i=k+1}^m \gamma_i\prod_{j=k+1}^{i-1}(1-w_j)w_i\\
		& \leq \gamma_k w_k' + (1-w_k')\sum_{i=k+1}^m \gamma_i\prod_{j=k+1}^{i-1}(1-w_j)w_i.
		\end{align*}
		Therefore, 
		\begin{align*}
		& f(A; w_1',...,w_{k-1}',w_k,w_{k+1},...,w_m)\\
		&=\sum_{i=1}^{k-1} \gamma_i\prod_{j=1}^{i-1}(1-w_j')w_i' + \prod_{j=1}^{k-1}(1-w_j')[\gamma_k w_k \\
		&\qquad +(1-w_k)\sum_{i=k+1}^{m}\gamma_{i}\prod_{j=k+1}^{i-1}(1-w_j)w_i]\\
		&\leq \sum_{i=1}^{k-1} \gamma_i\prod_{j=1}^{i-1}(1-w_j')w_i' + \prod_{j=1}^{k-1}(1-w_j')[\gamma_k w_k' \\
		&\qquad +(1-w_k')\sum_{i=k+1}^{m}\gamma_{i}\prod_{j=k+1}^{i-1}(1-w_j)w_i]\\
		&=f(A; w_1',...,w_{k-1}',w_{k}',w_{k+1},...,w_m).
		\end{align*}
		Then we obtain the result.
	\end{proof}

	\begin{lemma}
		\label{lem:estimateTech}
		Let $0 \leq p_1,...,p_K \leq 1$ and $u_1,...,u_K \geq 0$. Then
		\begin{align*}
		&~~\sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-\min\{p_i+u_i, 1\})\min\{p_k+u_k, 1\} \\
		& \leq \sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-p_i)p_k + \sum_{k=1}^K \gamma_k u_k.
		\end{align*}
	\end{lemma}
	\begin{proof}
		We prove this by induction. It holds obviously for $K=1$.
		\begin{align*}
		&~~\sum_{k=1}^{K+1} \gamma_k\prod_{i=1}^{k-1}(1-\min\{p_i+u_i, 1\})\min\{p_k+u_k, 1\} \\
		&\leq \sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-\min\{p_i+u_i, 1\})\min\{p_k+u_k, 1\}\\
		&+\gamma_{K+1}\prod_{i=1}^{K}(1-\min\{p_i+u_i, 1\})\min\{p_{K+1}+u_{K+1}, 1\}\\
		&\leq \sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-p_i)p_k + \sum_{k=1}^K \gamma_k u_k\\
		&+\gamma_{K+1}\prod_{i=1}^{K}(1-p_i)(p_{K+1}+u_{K+1})\\
		&\leq \sum_{k=1}^{K+1} \gamma_k\prod_{i=1}^{k-1}(1-p_i)p_k + \sum_{k=1}^{K+1} \gamma_k u_k
		\end{align*}
	\end{proof}

	\begin{lemma}
		With high probability $1-\delta$, $E[\Delta_{\bA_t}|\cH_t] \leq \frac{2}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$
	\end{lemma}
	\begin{proof}
		Using $f(\bA_t^*,\bU_t) \leq f(\bA_t,\bU_t)$, then
		\begin{align*}
		&\sum_{k=1}^{\abs{A_t^*}}\gamma_k (\prod_{i=1}^{k-1}(1 -\bU_t(a_{t,i}^*)))\bU_t(a_{t,k}^*) \\
		\leq &\sum_{k=1}^{\abs{\bA_t}}\gamma_k (\prod_{i=1}^{k-1}(1 -\bU_t(\ba_i^t)))\bU_t(\ba_k^t) 
		\end{align*}
		By lemma \ref{lem:estimateU} and lemma \ref{lem:increasing}, it holds that
		\begin{align*}
		&~~f(A_t^*, \theta_*^{\top}X_t) \\
		&\leq f(\bA_t, \min\{\theta_*^{\top}X_{t,a}+2\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}},1\}).
		\end{align*}
		Therefore by lemma \ref{lem:estimateTech},
		\begin{align*}
		&~~f(A_t^*, \theta_*^{\top}X_t) \\
		&\leq  \sum_{k=1}^{\abs{\bA_t}}\gamma_k (\prod_{i=1}^{k-1}(1 -\theta_*^{\top}X_{t,a_{t,i}^*})\theta_*^{\top}X_{t,a_{t,k}^*} \\
		&~~ + 2\sum_{k=1}^{\abs{\bA_t}}\gamma_k\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}\\
		&=f(\bA_t, \theta_*^{\top}X_t) + 2\beta_{t-1}(\delta)\sum_{k=1}^{\abs{\bA_t}}\gamma_k\norm{X_{t,a}}_{\bV_{t-1}^{-1}},
		\end{align*}
		which is equivalent to 
		$$
		\Delta_{\bA_t} \leq 2\sum_{k=1}^{\abs{\bA_t}}\gamma_k\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
		$$
	\end{proof}

@@
